Estimating the number of clusters using Cross Validation

### 2015-08-27 cvclust.tex
minor clarification

We have reduced the analysis of cross-validation error to the two-dimensional
case. In particular, following the calculations from the proof of
Prop.~\ref{prop:1clust-2dim}, if $|\corr(\rho^\T X, u_1^\T Y)| < 0.5$, then with
probability tending to one as $m$ and $n$ increase, $\CV(1) < \CV(2)$.
The condition $|\corr(\rho^\T X, u_1^\T)| < 0.5$ reduces to
\[
  \sum_{i=1}^p \rho_i^2 < 0.25.
\]
A sufficient (but not necessary) condition to ensure that this holds is that
the magnitude of the canonical correlation between the $X$ variables and
the $Y$ variables is below $0.5 / \sqrt{p}$.

>>>>

We have reduced the analysis of cross-validation error to the two-dimensional
case. In particular, following the calculations from the proof of
Prop.~\ref{prop:1clust-2dim}, if $|\corr(\rho^\T X, u_1^\T Y)| < 0.5$, then with
probability tending to one as $m$ and $n$ increase, $\CV(1) < \CV(2)$.
The condition $|\corr(\rho^\T X, u_1^\T)| < 0.5$ reduces to
\[
  \sum_{i=1}^p \rho_i^2 < 0.25.
\]
A sufficient (but not necessary) condition to ensure that this holds is that
the magnitude of the first canonical correlation between the $X$ variables and
the $Y$ variables is below $0.5 / \sqrt{p}$.
